---
title: "Bootstrap"
author: "Leihua Ye"
date: "9/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('boot',dep=TRUE)
library(boot)

mydata <- read.csv("Celtics_Heat_Game_6_Actual.csv")
mydata
```

```{r}
cor(mydata$X.Drafted,mydata$FPTS)
```

# Bootstrap the correlation between drafted and fantasy points 
# step 1: define a function that calculates the metric of interest 
```{r}
function_1 <- function(data, i){
	d2 <- data[i,] # for every row in the dataset
	return(cor(d2$X.Drafted, d2$FPTS))# calculate the correlationship between X.Drafted and FPTS
}
```

# step 2: fill in the dataset name, function, and the number oof bootstrap samples to be drawn 
```{r}
set.seed(1)
bootstrap_correlation <- boot(mydata,function_1,R=10000)
bootstrap_correlation
```

```{r}
summary(bootstrap_correlation)
```
t0: the observed values of k statistics applied to the original data 
t: An R*K matrix where each row is a bootstrap relicate of the k statistics

```{r}
range(bootstrap_correlation$t)
```

```{r}
mean(bootstrap_correlation$t)
```


```{r}
sd(bootstrap_correlation$t)
```
```{r}
class(bootstrap_correlation)
```
```{r}
boot.ci(boot.out=bootstrap_correlation,type=c('norm','basic','perc','bca'))
```
Four 95% confidence intervals are presented: normal, basic, percentile, and bias-corrected and accelerated. A fifth type, the studentized intervals, requires variances from each bootstrap sample.